On Cybersecurity\\Science and Engineering\footnote{Confidential, restricted to the authors. Property of V-Research S.r.l.}

### 2020-02-20 theory.tex
add intro to theory

\begin{enumerate}[noitemsep]
	\item cybersecurity as a requirement
	\item vulnerability\label{def:vulnerability}
\end{enumerate}

We describe processes, in our current formalization, in terms of the K-Modal
Structure as in Definition~\ref{def:modalinterpretation} (i.e. in terms of
causality principle).

\begin{definition}{\bf Vulnerability-Incident Process --}\label{def:vulnerability-incident}
	Given two 
\end{definition}

The whole-part relation \fix{mr}{(i.e.  HAS-A\footnote{HAS-A is just an hint for the
mechanization of this theory.  We'll come back to this in
Section~\ref{sec:implementation}})} is given, in the following, over the K Modal
logic described beforehand. To do so, we first need to formally define the
concept of \emph{agent} in its abstract form. We build it following the same
structure of\autocite{Santaca2016abf} but over the terms used in
Section~\ref{sec:problem}, i.e. knowledge, and belief as epistemic concepts. We'll then 
introduce the concept of \emph{intent} to define a \emph{threat agent}.

>>>>

In order to address the problem raised by Herley, 
we shall define how to distinguish between a secure and an insecure system.
While most of the literature (and this paper so far) have
correlated the problem of in-security to the maliciousness of
agents interacting with the system, we show that security
doesn't seem to have a malicious nature but, rather, insecurity 
raises from the lack of well-defined security requirements for the
design process of a system. We argue that the high number
of security vulnerability reported today are simply the realization
of potential system configurations, which deviate from the unintended 
behavior just because the intended behavior of the system is not precisely 
defined in the specification of the design process.

Given that the application of our theory is \emph{systems engineering} and that
the two foundational processes (exploitation and hacking) are based on the
concept of a system, we shall begin by defining what a system is, in its
abstract form.

\subsection{Abstract Systems}\label{sec:system}
The ISO/IEC/IEEE 15288:2015 (System Life Cycle Processes) 
provides a definition of system as ``A combination of interacting elements organized to
achieve one or more stated purposes.''\autocite{ISO201515288}.
Therefore, a system can be considered as a single agent where it's interacting
elements are the constituents of the agent itself. For the sake of simplicity
we first define a system as an agent and then extend the definition
to a ``combination of interacting'' agents.

We use the same process of \autocite{Santaca2016abf} but over slightly different
terms. The differences and commonalities with \autocite{Santaca2016abf} 
are described in Appendix~\ref{app:abf}. There is no 
agreement between the research communities (e.g. Multi-Agent-System, Epistemic Logic)
on which are the constituent of an agent as a system. However,
the same ideas revolved around for thousands of years. Some examples
follows.
\begin{itemize}
	\item In \autocite{Georgeoff1995bdi}, the BDI (Belief, Desire, Intent)
		paradigm is explained; where an agent can be defined over those
		three constituents.
	\item In \autocite{Hintikka1962knwoledge}, Hintikka describes the
		difference between Knowledge and Belief (as epistemological
		concepts), and the whole Doxastic logic defines in details how
		Beliefs can be formalized.
	\item In \autocite{Hintikka1993Information}, Hintikka describes the concept
		of Information and the difference with Knowledge and Belief.
	\item In \autocite{Empiricus1990Pyrrhonism}, the author states: ``The
		logical criterion also may be used in three senses -- of the
		agent, or the instrument, or the ``according to what''; the
		agent, for instance, may be a man, the instrument either sense
		perception or intelligence, and the ``according to what'' the
		application of the impression ``according to'' which the man
		proceeds to judge by means of one of the aforesaid
		instruments.'' 
	\item In \autocite{Santaca2016abf}, the authors defines an agent as a
		tuple of Assertions, Beliefs, and Facts.
\end{itemize}
